### 2017-05-06 paper/evaluation.tex
pass on rq6

This dimension assesses the impact of using distinct parallel
configurations on test flakiness (negative impact) and speedup
(positive impact).  Recall that increased resource contention obtained
with parallelism can lead to concurrency issues such as data races.
Flakiness and speedup are contradictory forces that drive
configuration selection.  Furthermore, note that Section~\ref{sec:rqD}
evaluated speedup in isolation, focused on projects configured to use
parallelism by default.

@@

To answer this research question, we conducted an experiment involving
the six parallel configurations from Section~\ref{sec:modes}  and the
top 10 projects with long-running tests suites from our sample set. We
are interested in understanding how efficiency (\ie, testing cost) and
flakiness (\ie, failing tests) are affected when we run a test suite
with different parallel configurations. \Jbc{I think we must have a
sentence to motivate why we want to understand this relationship}.  We
used as a \emph{control group} (\ie, baseline) the sequential
execution of each subject's tests. Notice that for measuring
flakiness, we have to consider only tests that failed due to the
concurrency in the parallel execution. To this purpose, we re-executed
the tests in sequence ten times and carefully verified that there are
only passing tests in our baseline. We considered ten as the number of
re-executions based on the approach used by Google reported in a
previous work on test flakiness~\cite{luo-etal-fse2014}. For the
parallelism configurations, we implemented a script that takes a
subject and a configuration (\eg, \ForkSeq{}) as inputs, and the
script outputs the modified version of the subject with the desired
configuration. The workflow consists in copying the project directory
to a new directory, finding all existing build files (\ie, \pomf{}
files), and modifying all existing Maven Surefire configurations with
new values for the parameters \CodeIn{parallel}, \CodeIn{forkCount},
and \CodeIn{threadCount} using an XPath~\cite{xpath} library to
manipulate XML documents. For configurations with forked JVMs enabled
(\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
\CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per core).
To adjust the pool of threads for parallelism within a JVM, we changed
the parameter \CodeIn{threadCount} with \Jbc{should we consider 2 as
it is the number of native threads per core OR 6 as it represents 3
Cores * 2 native threads?}.  To run the subjects and their respective
variations (\ie, the modified versions according to the parallelism
configuration), we used a similar approach as in
Figure~\ref{fig:mvn-execution} except that we added a timeout of one
hour to run the tests. We used the \CodeIn{timeout}
command~\cite{timeout-cmd} to monitor the execution, and we configured
the command to dispatch a \emph{kill} signal if the test execution
exceeds the time limit. We imposed this time constraint to avoid
hanging indefinitely the experiment execution due to some thread
contention that may occur (\eg, deadlock). Finally, we saved each
execution log and XML test reports generated by Maven to collect the
execution time, the number of failing tests, and for reference to
analyze and diagnose outliers in our results. For efficiency, we
reported the speedup (\ie, $T_{\text{s}} / T_{\text{p}}$) in average,
and for flakiness, we reported the rate of failing tests (\ie,
$\mathit{\%_\text{fail} = failures / tests}$) in average.
Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
the time cost (\ie, $T_\text{cost}$).

%% that satisfies the following criteria: (1) tests run in sequence by
%% default and (2) test suite consists only by passing tests. The first
%% criteria is to use the default execution (\ie, configuration \Seq{})
%% as a baseline to compare speedup with the other parallel
%% configurations. The second criteria is to avoid introducing noise when
%% measuring the rate of flakiness caused by the non-deterministic
%% execution of tests. We are interested only in failures manifested when
%% parallelism is enabled. Since the number of failing tests may vary, we
%% run each project three times and report the average elapsed time and
%% rate of flakiness.

@@

\begin{figure*}[t]
\centering
\small
\begin{tabular}{l|rr|rrrrrrrrrr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
OpenMRS Core (\CodeIn{api})  & \entry{13.8m}{3436} & \entry{-}{58.7\%}     & \entry{1.86x}{65.6\%} & \entry{2.01x}{61.6\%} & \entry{1.51x}{0\%} & \colheader{\cellcolor{lightgray}JVM Crash}\\%
Apache Flume (\CodeIn{core}) & \entry{8.3m}{392}   & \entry{2.82x}{18.1\%} & \entry{-}{0\%} & \entry{2.78x}{16.8\%} & \entry{-}{0\%} & \entry{2.87x}{18.9\%}\\%
Apache Giraph (\CodeIn{core})& \entry{7m}{236}     & \entry{2.08x}{5.1\%}  & \colheader{\cellcolor{lightgray}JVM Crash}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
Struct (\CodeIn{rest})       & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%

%% Linkedin Pinot & 3480.091s & 1703.958s & 24.726s & 2229.822s & 783.12s & 761.973s\\%
%% Linkedin Pinot & 58m & 2.04x & 140x & 1.56x & 4.44x & 4.56x\\%
%% Jenkins CI Github Plugin & 3298.603s & 2049.709s & 1547.261s & 1240.544s & 2975.232s & 227.214s \\%
%% Jenkins CI Github Plugin & 55m & 1.60x & 2.13x & 2.65x & 1.10x & 14.51x \\%
%% Kite SDK & - & - & - & - & - & -\\%
%% Apache Giraph & 1041.884s & 37.666s & 116.78s & 1037.105s & 1038.39s & 45.992s\\%
%% Apache Giraph & 17.36m & 27.66x & 8.92x & 1.00x & 1.00x & 22.65x\\%
%% OpenMRS Core & - & - & - & - & - & -\\%
%% Jenkins CI Docker Workflow Plugin & 447.069s & 490.675s & 27.69s & 8.244s & 439.207s & 38.3s\\%
%% Jenkins CI Docker Workflow Plugin & 7.45m & 0.91x & 16.14x & 54.22x & 1.01x & 11.67x\\%
%% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
%% Geotools & 8.41m & - & - & - & - & -\\%
%% Atomix & 7.78m & - & - & - & - & -\\%
%% Kuromoji & 7.68m & - & - & - & - & -\\%
%%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
%%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%

@@

%%To evaluate the distribution of execution time per project, we sorted
%%the test cases by decreasing order of elapsed time and calculated the
%%number of tests executed in 90\% of the total time. Later, we reported
%%the \Fix{balance} of execution time by dividing the number of tests
%%that represents 90\% of the execution time by the number of tests
%%cases. For instance, a balance of 50\% indicates \Fix{...}.  \Fix{We
%%collected the elapsed time from test cases for each generated report.
%%Maven Surefire generates an XML report with execution information
%%(\eg, number of skipped tests and elapsed time) per test suite
%%\Jbc{Should I use the previous sentence as a footnote or should I
%%delete it?}. We noticed that some test cases reported an elapsed time
%%of zero: since the reported time is in milliseconds, some tests may
%%execute in a shorter time. \Fix{..to be continued...}}. Results
%%indicate that \Fix{...}.
%%
%%\begin{figure}[h!]
%%    \centering
%%    \includegraphics[width=0.4\textwidth]{results/plots/balance.pdf}
%%    \caption{\Fix{balance}}
%%\end{figure}

%% \subsection{Answering research question RQ3}
%% \label{sec:rqThree}
%% 
%% \begin{itemize}
%%     \item \RQB
%% \end{itemize}
%% 
%% To evaluate the distribution of CPU and IO intensive test suites from
%% the sample set, we used the command \emph{sar} to monitor the system
%% activity in background while tests ran. \emph{Sar} is a command that
%% collects and reports statistics (\eg, percentage of IO waiting and
%% usage of CPU in user mode) based on the kernel activity and it is
%% highly configurable to collect detailed information (\eg, usage of a
%% specific processor core or percentage of network interface
%% utilization). We configured \emph{sar} to report \Fix{...explain how
%% we executed and what fields we are interested}. \Fix{explain fields}.
%% Figure \Fix{A} shows the distribution of subjects grouped in intervals
%% of \Fix{W}\% of CPU utilization. Results indicates that \Fix{...}
%% 
%% \begin{figure}[h!]
%%     \centering
%%     \includegraphics[width=0.4\textwidth]{results/plots/cpuness.pdf}
%%     \caption{\Fix{cpu usage}}
%% \end{figure}
%% 
%% \Comment{we proposed the definition of \emph{cpuness}
%% computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
%% where \emph{user\_t} is the elapsed time of execution in \emph{user
%% mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
%% \emph{elapsed\_t} is the elapsed time to finish the execution. We
%% measured the \emph{cpuness} of each regression test \Fix{...elaborate
%% the meaning of cpuness} \Fix{Describe how I measured user, system and
%% "wall" time}.  \Fix{Explain results}.  \Fix{show plots}}
%%

>>>>

This dimension assesses the impact of using distinct parallel
configurations on test flakiness (negative impact) and speedup
(positive impact).  Furthermore, note that Section~\ref{sec:rqD}
evaluated speedup in isolation, focused on projects configured to use
parallelism by default.

@@

To answer this research question, we conducted an experiment involving
the six parallel configurations from Section~\ref{sec:modes}  and the
top 10 long-running test modules from our sample
set. The rationale for this selection criteria was to maximize the
chances of observing speedup and flakiness, assuming that long-running
tests also have many tests. Indeed, we confirmed that test suites in
these projects contain at least \Fix{X} tests. Also, we preferred to
compare the effect of a configuration over a single test module for
projects with multiple test modules.  Recall that large projects may
contain several test modules, and these modules may contain distinct
characteristics that could favor one configuration and not others;
therefore, it would be necessary to check each module individually for
a fair comparison.  We are interested in understanding how efficiency
(\ie, testing cost) and flakiness (\ie, failing tests) are affected
when we run a test suite with different parallel configurations.
Recall that increased resource contention obtained with parallelism
can lead to concurrency issues such as data races.  Flakiness and
speedup are contradictory forces that drive configuration selection.
We used as a \emph{control group} (\ie, baseline) the sequential
execution of each subject's tests. Notice that for measuring
flakiness, we have to consider only tests that failed due to the
concurrency in the parallel execution.  For that reason, we
re-executed the tests in sequence ten times and carefully verified
that there are only passing tests in our baseline.  We considered ten
as the number of re-executions based on the approach used by Google
reported in a previous work on test flakiness~\cite{luo-etal-fse2014}.
To obtain parallel configurations, we implemented a script that takes
a subject and a configuration (\eg, \ForkSeq{}) as inputs, and the
script outputs the modified version of the subject with the desired
configuration. The workflow consists in copying the project directory
to a new directory, finding all existing build files (\ie, \pomf{}
files), and modifying all existing Maven Surefire configurations with
new values for the parameters \CodeIn{parallel}, \CodeIn{forkCount},
and \CodeIn{threadCount} using an XPath~\cite{xpath} library to
manipulate XML documents. For configurations with forked JVMs enabled
(\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
\CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per core).
To adjust the pool of threads for parallelism within a JVM, we changed
the parameter \CodeIn{threadCount} with \Jbc{should we consider 2 as
it is the number of native threads per core OR 6 as it represents 3
Cores * 2 native threads?}.  To run the subjects and their respective
variations (\ie, the modified versions according to the parallelism
configuration), we used a similar approach as described in
Figure~\ref{fig:mvn-execution} except that we added a timeout of one
hour to run the tests. We used the \CodeIn{timeout}
command~\cite{timeout-cmd} to monitor the execution, and we configured
the command to dispatch a \emph{kill} signal if the test execution
exceeds the time limit. We imposed this time constraint to avoid
hanging indefinitely the experiment execution due to some thread
contention that may occur (\eg, deadlock). Finally, we saved each
execution log and XML test reports generated by Maven to collect the
execution time, the number of failing tests, and for reference to
analyze and diagnose outliers in our results. For efficiency, we
reported the speedup (\ie, $\Uparrow_\text{speed} = T_{\text{s}} /
T_{\text{p}}$) in average, and for flakiness, we reported the rate of
failing tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$) in
average.  Figure~\ref{tab:rq6-table} summarizes the obtained results
ordered by the time cost (\ie, $T_\text{cost}$).

@@

\begin{figure*}[t]
\centering
\small
\begin{tabular}{l|rr|rrrrrrrrrr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
OpenMRS Core (\CodeIn{api})  & \entry{13.8m}{3436} & \entry{-}{58.7\%}     & \entry{1.86x}{65.6\%} & \entry{2.01x}{61.6\%} & \entry{1.51x}{0\%} & \colheader{\cellcolor{lightgray}JVM Crash}\\%
Jankotek MapDB               & \entry{10m}{5218}   & \multicolumn{6}{c}{\cellcolor{lightgray}\emph{JVM Crash}} & \entry{3.9x}{0\%} & \colheader{\cellcolor{lightgray}timeout}\\%
Apache Flume (\CodeIn{core}) & \entry{8.3m}{392}   & \entry{2.86x}{18.1\%} & \entry{-}{0\%} & \entry{2.78x}{16.8\%} & \entry{-}{0\%} & \entry{2.87x}{18.9\%}\\%
Apache Giraph (\CodeIn{core})& \entry{7m}{236}     & \entry{2.08x}{5.1\%}  & \colheader{\cellcolor{lightgray}timeout}  & \entry{-}{0\%} & \entry{-}{0}\% & \colheader{\cellcolor{lightgray}JVM Crash}\\%
Stripe Java                  & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
Facebook Archive Linkbench   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
%% Jenkins CI Github            & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
%% Jenkins CI Docker Workflow   & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%
%% Hazelcast                    & \entry{Xm}{Z}       & \entry{x}{\%}          & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%} & \entry{x}{\%}\\%

@@
